\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities \red{(Section XXX)}; (b) the collapse of fluid interfaces through the use of adaptive mesh grid \red{(Section XXX)}; (c) the impact of viscosity ratios on the formation and progress of fingers \red{(Section XXX)}.

@@

%%%%%%%%%%%%%
\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}

@@

\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}

>>>>

In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt} ; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete} ; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{}.

@@

%%%%%%%%%%%%%
\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}\label{section:results_hete_fix_adapt}

@@

\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}\label{Section:results_dinlet}
